A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-09 12_conclusions_future_work.tex
describe implications on full model (reviewer 3.12)

The proposed beading scheme greatly improves the process planning for parts with thin contours, which often occur for example in architectural models, prototypes for casings or microstructures.
Meanwhile it leaves most of the toolpaths the same as the uniform width technique in large features, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards most of the nozzle size considerations.}

>>>>

The proposed beading scheme greatly improves the process planning for parts with thin contours, which often occur for example in architectural models, prototypes for casings or microstructures.
Meanwhile it leaves most of the toolpaths the same as the uniform width technique in large features, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
\revise{}{Compared to the naive approach of constant width toolpaths our beading scheme improves the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
